\Large{\textbf{A biophysical minimal model to investigate age-related changes in CA1 pyramidal cell electrical activity}}

### 2023-09-08 paper/article.tex
Update Zenodo DOI

\subsection{Resource availability}
Resources generated by this study (code, figures, and manuscript files) are available via GitHub (\href{https://github.com/emckiernan/agingCA1}{github.com/emckiernan/agingCA1}) and archived via Zenodo (\href{https://doi.org/10.5281/zenodo.6788230}{doi.org/10.5281/zenodo.6788230}). To facilitate reuse, resources are shared under open licenses (see the license file in our GitHub repository). To promote reproducibility, Python code is embedded in a Jupyter notebook \cite{kluyver2016jupyter} that explains the code, how to use it, and how to generate the figures herein, plus additional ones.

>>>>

\subsection{Resource availability}
Resources generated by this study (code, figures, and manuscript files) are available via GitHub (\href{https://github.com/emckiernan/agingCA1}{github.com/emckiernan/agingCA1}) and archived via Zenodo (\href{https://doi.org/10.5281/zenodo.6788229}{doi.org/10.5281/zenodo.6788229}). To facilitate reuse, resources are shared under open licenses (see the license file in our GitHub repository). To promote reproducibility, Python code is embedded in a Jupyter notebook \cite{kluyver2016jupyter} that explains the code, how to use it, and how to generate the figures herein, plus additional ones.
